### 2025-05-15 docs/Homeownership_BankOfMomAndDad.tex
Post-QJE Revision (#11)
* Update data through 2021 (not, code not return, but model implications are tiny!)

* Show less subgroups for the summary statistics table

* Include more and better transfer/inheritance data

* Add new empirical results on ownership retention

* Added more non-targeted moments

* Updated text 
---------

Co-authored-by: Eirik Eylands Brandsaas <eirik.e.brandsaas@frb.gov>

The exercise follows \cite{Chetty2007} closely. The outcome of interest is the change in log housing consumption, which is set to zero for households who do not move. For movers, housing consumption is defined as yearly rent while renting and as imputed rent for owners, set to 5\% of the market value \citep{Davis2008}. The sample is limited to household heads who experience only one unemployement spell between ages 25 and 44. I divide the sample by whether a household's parents were in the top parental wealth quartile at the time of unemployment and compare the two groups' housing consumption growth at unemployment. The results are displayed in Figure \ref{fig:housinggrowthrates}. Among households with non-wealthy parents, housing consumption falls by about 5\% during unemployment ($p<0.05$). In contrast, households with wealthy parents see a slight increase (not significant) in housing consumption during unemployment. As shown in Appendix~\ref{app:eventstudy_details}, the main finding---that households with wealthy parents do not downsize during unemployment---is also retained in a formal event study that includes the same set of controls as the previous regressions. I return to these results later as part of the model validation.

>>>>

The exercise follows \cite{Chetty2007} closely. The outcome of interest is the change in log housing consumption, which is set to zero for households who do not move. For movers, housing consumption is defined as yearly rent while renting and as imputed rent for owners, set to 5\% of the market value \citep{Davis2008}. The sample is limited to household heads who experience only one unemployement spell between ages 25 and 44. I divide the sample by whether a household's parents were in the top parental wealth quartile at the time of unemployment and compare the two groups' housing consumption growth at unemployment. The results are displayed in Figure \ref{fig:housinggrowthrates}. Among households with non-wealthy parents, housing consumption falls by about 5\% during unemployment ($p<0.05$). In contrast, households with wealthy parents see a slight increase (not significant) in housing consumption during unemployment. Appendix~\ref{app:eventstudy_details} shows that these patterns are robust to an event-study specification that controls for household characteristics. I return to these results later as part of the model validation.
